A generic and fast C++ optimization framework

### 2017-10-21 paper.tex
Add simple optimizer class.

\begin{minted}{c++}
  template<bool UseKernel, typename KernelType, typename MatType>
  class MeanShift;
\end{minted}

@@

\begin{minted}{c++}
  MeanShift<true, GaussianKernel, arma::mat>
\end{minted}

@@

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{c++}
class ObjectiveFunction {
 ObjectiveFunction() {
  in = arma::vec("20 12 15 100");
  bi = arma::vec("-4 -2 -3 -8");
 }

@@

 arma::vec in, bi; arma::uvec order;
}
\end{minted}
\caption{Simple objective function where each dimension has a parabola with a
  distinct minimum}
\end{listing}
\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{c++}
class SimpleOptimizer {
 SimpleOptimizer(size_t bs = 2, double lr = 0.1) : bs(bs), lr(lr) {}

 template<typename FunctionType>
 double Optimize(FunctionType& function, arma::mat& parameter) {
  arma::mat gradient;
  for (size_t i = 0; i < 300; ++i)
  {
   const size_t funIdx = i % 4;
   function.Gradient(parameter, funIdx, gradient, batchSize);
   parameter -= lr * gradient;

   function.Shuffel();
  }

  return function.Evaluate(parameter, 0, function.NumFunctions());
 }
 size_t bs;  double lr;
}
\end{minted}
\caption{Simple stochastic gradient descent method with a static number of
iterations to optimize the function parameter ({\tt bs} defines the batch size
and {\tt lr} the learning rate). )}
\end{listing}

Using this code, we can compile the code, and when we run it we receive the
following output:

>>>>

\begin{minted}[fontsize=\footnotesize]{c++}
  template<bool UseKernel, typename KernelType, typename MatType>
  class MeanShift;
\end{minted}

@@

\begin{minted}[fontsize=\footnotesize]{c++}
  MeanShift<true, GaussianKernel, arma::mat>
\end{minted}

@@

% \vspace*{-0.3em}
\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{c++}
class ObjectiveFunction {
 ObjectiveFunction() {
  in = arma::vec("20 12 15 100");
  bi = arma::vec("-4 -2 -3 -8");
 }

@@

 arma::vec in, bi; arma::uvec order;
}
\end{minted}
\vspace{-0.6em}
\caption{Simple objective function where each dimension has a parabola with a
  distinct minimum}
\vspace{-0.8em}
\end{listing}
\vspace{-0.8em}
\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{c++}
class SimpleOptimizer {
 SimpleOptimizer(size_t bs = 2, double lr = 0.1) : bs(bs), lr(lr) { }

 template<typename FunctionType>
 double Optimize(FunctionType& function, arma::mat& parameter) {
  arma::mat gradient;
  for (size_t i = 0; i < 300; ++i) {
   const size_t funIdx = i % 4;
   function.Gradient(parameter, funIdx, gradient, batchSize);
   parameter -= lr * gradient;
   function.Shuffel();
  }
  return function.Evaluate(parameter, 0, function.NumFunctions());
 }
 size_t bs;  double lr;
}
\end{minted}
\vspace{-0.6em}
\caption{Simple stochastic gradient descent method with a static number of
iterations to optimize the function parameter ({\tt bs} defines the batch size
and {\tt lr} the learning rate). )}
\vspace{-0.6em}
\end{listing}
\vspace{-0.8em}
Using this code, we can compile the code, and when we run it

\begin{minted}[fontsize=\footnotesize]{c++}
ObjectiveFunction function; arma::mat parmeter("0 0 0 0;")
SimpleOptimizer optimizer;
std::cout << optimizer.Optimize(function, parameter);
\end{minted}
we receive the following output:
